The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-06-17 WavesData-2019/LatexNotes/notes.tex
NMM
NM

% New
\newcommand{\Hp}{H^{+}}
\newcommand{\Hm}{H^{-}}
\newcommand{\Gp}{\Gibbs^{+}}
\newcommand{\Gm}{\Gibbs^{-}}

@@

The dimensionless KdV equation is
\begin{align}
\label{varKdV}
u_t + \ampp D^{-3/2} \, u u_x + \mu D^{1/2} \, u_{xxx} = 0
\end{align}
with the dimensionless parameters
\begin{align}
\ampp = \eps \delta^{-2} = \frac{ag}{h_0^2 f_p^2} , \qquad
\mu = \frac{4 \pi^2}{9 \lamfac^2}
\end{align}
Here, $\lamfac$ is the number of peak wavelengths in the periodic domain (perhaps we should set $\lamfac=1$, see note below). Above, the displacement $u$ has been scaled on the characteristic wave amplitude $a = \mean{\eta^2}^{1/2}$, and position $x$ has been scaled on the upstream characteristic wavelength $\lambda_0 = \sqrt{g h_0}/f_p$.
Then the Hamiltonian is given by
\begin{align}
\label{Hamiltonian}
& \Hm = \ampp H_3 - \mu H_2 \\
& \Hp = \ampp D_0^{-3/2} H_3 - \mu D_0^{1/2} H_2
\end{align}
where
\begin{align}
&H_3 = \intt u^3 \dx	\, , \\
&H_2 = \intt u_x^2 \dx	\, .
\end{align}

@@

The statistical matching condition is
\begin{equation}
\mean{\Hp}_{\Gm} = \mean{\Hp}_{\Gp}
\end{equation}

>>>>

% New
\newcommand{\Hp}{H^{+}}
\newcommand{\Hm}{H^{-}}
\newcommand{\Gp}{\Gibbs^{+}}
\newcommand{\Gm}{\Gibbs^{-}}
\newcommand{\meanp}[1]{\mean{#1}_{+}}
\newcommand{\meanm}[1]{\mean{#1}_{-}}

@@

The dimensionless KdV equation is
\begin{align}
\label{varKdV}
u_t + \ampp D^{-3/2} \, u u_x + \mu D^{1/2} \, u_{xxx} = 0
\end{align}
with the dimensionless parameters
\begin{align}
\label{ndKdV}
\ampp = \eps \delta^{-2} = \frac{ag}{h_0^2 f_p^2} , \qquad
\mu = \frac{4 \pi^2}{9 \lamfac^2}
\end{align}
Here, the displacement has been scaled on the characteristic wave amplitude, $u = \eta/a$, where $a = \etastd= \mean{\eta^2}^{1/2}$.
Position $x$ has been scaled on the upstream characteristic wavelength $\lambda_0 = \sqrt{g h_0}/f_p$. As a consequence of the scaling for displacement, we have fixed energy
\begin{equation}
\frac{1}{2} \intt u^2 \dx = \frac{1}{2}
\end{equation}

In \eqref{ndKdV} , $\lamfac$ is the number of peak wavelengths in the periodic domain (perhaps we should set $\lamfac=1$, see note below).
Then the Hamiltonian is given by
\begin{align}
\label{Hamiltonian}
& \Hm = \ampp H_3 - \mu H_2 \\
& \Hp = \ampp D_0^{-3/2} H_3 - \mu D_0^{1/2} H_2
\end{align}
where
\begin{align}
&H_3 = \frac{1}{6} \intt u^3 \dx	\, , \\
&H_2 = \frac{1}{2} \intt u_x^2 \dx	\, .
\end{align}

@@

The statistical matching condition is
\begin{equation}
\meanm{\Hp} = \meanp{\Hp}
\end{equation}
An experimental observation is that the incoming skewness is small, thus
\begin{equation}
\meanm{H_3} \approx 0
\end{equation}
which immediately gives
\begin{equation}
\ampp D_0^{-3/2} \meanp{H_3} = \mu D_0^{1/2} \left( \meanp{H_2} - \meanm{H_2} \right)
\end{equation}
